Extreme Value Chapter 3

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Cleaning up. Ready to run the other scenarios.

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = " ", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw(base_size = 8) +
  theme(legend.position = "right") -> b

@@

GP_mles %>% 
    mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Generalized Pareto") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none") -> c

@@

```{r Fig4, fig.width=12, fig.height=5}

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
  facet_wrap(~labelsamp, nrow = 2) +
  geom_boxplot() +
  scale_color_manual(values = pal_mixture[c(1,4)], name = "Bias") +
  scale_fill_manual(values = pal_mixture[c(2,3)], name = "Bias") +
  geom_hline(yintercept = 0, color = "red") +
  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
  theme_bw()
ggsave("Ch3_samplesize/Figures/Figure4.png")
```

>>>>

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = " ", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
  theme_bw(base_size = 8) +
  theme(legend.position = "right") -> b

@@

GP_mles %>% 
    mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Generalized Pareto") +
  theme_bw(base_size = 8) +
  theme(legend.position = "none") -> c

@@

```{r Fig4, fig.width=6, fig.height=6}

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
  facet_wrap(~labelsamp, nrow = 3) +
  geom_boxplot() +
  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
  theme_bw()
ggsave("Ch3_samplesize/Figures/Figure4.png")
```
